Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-14 paper/main.tex
Finished overhead results

\paragraph{Cython bindings}
To eliminate as much as possible of overhead introduced by our bindings, we
timed the calls from our bindings to the underlying C-function. The overhead
should be the same for all bindings, since the Cython code is the same. The
measured overhead, calculated from BLAKE can be seen in Table XX.

@@

\paragraph{Modification to Tahoe-\ac{LAFS}}
Because we write to two files after each hash calculation, this will create an
overhead in the measurements that would not normaly exist in Tahoe-\ac{LAFS}.
This overhead should be about the same for all candidates, since the number of
writes are equal. The results and calculations for this overhead, based on runs
with double \ac{SHA}-256 can be seen in Table XX.

>>>>

\paragraph{Cython bindings}
To eliminate as much as possible of overhead introduced by our bindings, we
timed the calls from our bindings to the underlying C-function. The overhead
should be the same for all bindings, since the Cython code is the same. The
measured overhead, calculated from BLAKE can be seen in Table
\ref{tbl:cython:overhead}.

@@

\paragraph{Modification to Tahoe-\ac{LAFS}}
Because we write to two files after each hash calculation, this will create an
overhead in the measurements that would not normaly exist in Tahoe-\ac{LAFS}.
This overhead should be about the same for all candidates, since the number of
writes are equal. The results and calculations for this overhead, based on runs
with double \ac{SHA}-256 can be seen in Table \ref{tbl:measure:overhead}.

\input{tables/measure_overhead}
